\documentclass[11pt,fullpage]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{listliketab}
\usepackage{array}
\usepackage{longtable}

\usepackage{natbib}
\usepackage{bibentry}
\nobibliography*
%\bibliographystyle{apa}

% Palatino font
%\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo}

\usepackage[utf8]{inputenc}
\def\name{Matthieu Laneuville (Research Scientist)}

\reversemarginpar

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}
\bibliographystyle{apalike}

% Print name centered and bold:
\centerline{\Large \bf \name}

\vspace{0.25in}

\begin{minipage}{0.50\linewidth}
\href{http://elsi.jp/en/}{Earth-Life Science Institute} \\
  	Tokyo Institute of Technology \\
	2-12-1-IE-1 Ookayama, Meguro-ku \\
	Tokyo, 152-8550, Japan \\
\end{minipage}
\begin{minipage}{0.50\linewidth}
  \begin{tabular}{ll}
    Phone: & +81 (0)3 57 34 27 15 \\
    Email: & \href{mailto:mlaneuville@gmail.com}{mlaneuville@gmail.com} \\
    Homepage: & \href{http://mlaneuville.github.io}{http://mlaneuville.github.io} \\
  \end{tabular}
\end{minipage}

\section*{Education}

\begin{longtable}{p{0.7in}|p{5.5in}}
	2010--2013 & {\bf Ph.D.} Geophysics, Institut de Physique du Globe de Paris (IPGP) \\
	2008--2010 & {\bf M.Sc.} Physics, Université Pierre et Marie Curie (UPMC), Paris \\
	2005--2008 & {\bf B.Sc.} Physics, Université de Provence I \\
\end{longtable}

\section*{Publications}

\setlength{\extrarowheight}{10pt}

\begin{longtable}{p{0.3in}|p{5.5in}}
  2015 & \bibentry{BocanegraBahamon:2015dp} \\
	  & \bibentry{Guttenberg:2015wh} \\
  2014 & \bibentry{Laneuville:2014el} \\
	  & \bibentry{Arridge:2014ho} \\
  2013 & \bibentry{Laneuville:2013gp} \\
	  & \bibentry{Miljkovic:2013uw}\\ 
  2011 & \bibentry{LeBars:2012hc} \\
       	  & \bibentry{Grott:2011hl} \\
\end{longtable}

\section*{Conference Oral Presentations}

\begin{longtable}{p{0.3in}|p{5.5in}}
	2014 & \emph{A long-lived lunar dynamo powered by core crystallization}, in Lunar and Planetary Science 
Conference (LPSC), Houston, US. \\
	2013 & \emph{Asymmetric Thermo-Chemical Evolution of the Moon}, in Lunar and Planetary Science
Conference (LPSC), Houston, US. \\
	2012 & \emph{Asymmetric thermal evolution of the Moon}, in Geodynamics Workshop, Wandlitz, Germany. \\
	2012 & \emph{Asymmetric thermal evolution of the Moon}, in Planetary Volcanism Workshop, Toulouse, France. \\
	2010 & \emph{Thermo-chemical evolution and global contraction of Mercury}, in European Planetary
Science Congress (EPSC), Rome, Italy.
\end{longtable}

\setlength{\extrarowheight}{5pt}

\section*{Grants}

\begin{longtable}{p{0.3in}|p{5.5in}}

 2013 & PI of DARI Proposal for Supercomputer access (80k hours) \\
 2013 & Co-PI of HLRN Supercomputer access (1.2M hours) \\
 2012 & PI of DARI Proposal for Supercomputer access (80k hours) \\
 2012 & Co-PI of JSC Supercomputer access (384k hours) \\
 2012 & CNES Alpbach Summer School Fellow (1100 EUR) \\

\end{longtable}

%\section*{Additional Papers Presented at Professional Meetings}

%Bergey CM & Patel ER (2007, November). The vocal repertoire of the greater bamboo lemur.
%Presentation at the American Embassy in Antananarivo, Madagascar.

\section*{Teaching Experience and Public Outreach}

\begin{longtable}{p{0.7in}|p{5.5in}}

	2015 & \textbf{Article} review article on lunar history for French newspaper (in prep). \\
	2014 & \textbf{Interwiew} 3 interventions on lunar evolution for French and German newspaper. \\

	2011 & \textbf{Teaching assistant} for ``Computing tools'' University Paris Diderot (Paris 7) \\ 

	2010 & \textbf{Teaching assistant} for ``Mathématiques 2'', Prof. S. Jacquemoud (Institut de Physique
du Globe de Paris) \\ 

	2009 & \textbf{Public outreach}. Participation in the 40th anniversary commemoration of the Apollo 11
Moon landing (Clair de Lune). \\

\end{longtable}


% Footer
\bigskip
\begin{center}
  \begin{footnotesize}
    Last updated: \today
  \end{footnotesize}
\end{center}

\nobibliography{library}

\end{document}
